Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-12 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Added Ali2019 as an example for SSCM. Searching for additional examples ...

SICM and confocal FM have been combined for the first time by Korchev et al.
\cite{Korchev2000} in 2000. The group used this combination to verify the
volume measurements obtained by SICM. Just a year later, further development
of this combination enabled simultaneous acqusition of Ca\textsuperscript{2+}
imaging and topography data \cite{Shevchuk2001}.
% Afterwards, many different
% studies using a combination of SICM and confocal FM were published:

@@

% Bis hier

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating the
dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells 
(figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent nanoparticles in 
immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells \cite{Kemp2008} and for 
investigating the differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been utilized
in studies investigating endocytotic pathways \cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and in
a study investigating an alternative closing mechanism for clathrin-coated pits (CCPs) by recording 
topography simultaneously with the fluorescence of actin-binding protein-green fluorescent protein 
(Abp1-GFP) and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}.
In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized human
alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.

>>>>

SICM and confocal FM have been combined for the first time by Korchev et al.
\cite{Korchev2000} in 2000. The group used this combination to verify the
volume measurements obtained by SICM. Just a year later, further development
of this combination enabled simultaneous acquisition of Ca\textsuperscript{2+}
imaging and topography data \cite{Shevchuk2001}.
% Afterwards, many different
% studies using a combination of SICM and confocal FM were published:

@@

% Bis hier
% Bitoun2005 -> PMID: 16227997; Zuechner2005 -> PMID: 15731758; Ali2019 -> PMID: 31017801
% Added: Ali2019 -> ich suche noch nach weiteren Beispielen

To highlight the versatility of SSCM, here are some examples: SSCM has been used for investigating 
the dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 
cells (figure \ref{fig:sicm+scm}b,d), for the investigating the uptake of fluorescent 
nanoparticles in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 cells 
\cite{Kemp2008} and for investigating the differentiation of stem cells \cite{Gorelik2008}. 
Furthermore, it has been utilized in studies investigating endocytotic pathways 
\cite{Shevchuk2008} (figure \ref{fig:sicm+scm}c) and \cite{Shevchuk2012,Ali2019}. In the study of 
Shevchuk et al. \cite{Shevchuk2012} in 2012 an alternative closing mechanism for clathrin-coated 
pits (CCPs) were found by recording topography simultaneously with the fluorescence of actin-
binding protein-green fluorescent protein (Abp1-GFP) and clathrin light-chain-enhanced green 
fluorescent protein (Clc-EGFP) \cite{Shevchuk2012}. In the study of Ali et al. \cite{Ali2019} the 
effect of mutations in the Dynamin 2 (DNM2) gene, which play a role in diseases like centronuclear 
myopathy \cite{Bitoun2005} or Charcot-Marie-Tooth disease \cite{Zuechner2005}, on the morphology 
and the kinetics of the uptake-relevant processes -- formation, internalization … -- of CCPs were
investigated.

In another study the uptake of 200~nm fluorescent, carboxylated latex particles into immortalized 
human alveolar epithelial type 1-like (AT1) cells was investigated by SSCM \cite{Novak2014}.
